### 2022-05-13 main/chapter_2ljets.tex
add discovery region results table

Our central result is Figure~\ref{fig:2ljets_summary}, which shows the names,
data, and fitted background expectations with error bars in all main regions.
This figure illustrates the background-model part of a \clown{likelihood}
function which is extended with signals to test alternative models.
Exclusion contours testing the addition of C1N2 and GMSB signals to these
backgrounds are shown in Figure~\ref{fig:2ljets_contours}.

@@

\begin{figure}[tp]
\centering
\begin{subfigure}{\textwidth}
    \centering
    \includegraphics[width=0.7\textwidth]{figures/2ljets_contours_c1n2.pdf}
    \caption{C1N2 contours}
\end{subfigure}
\\[1em]
\begin{subfigure}{\textwidth}
    \centering
    \includegraphics[width=0.7\textwidth]{figures/2ljets_contours_gmsb.pdf}
    \caption{GMSB contours}
\end{subfigure}
\caption{%
Contours from the $\twoljets$ electroweak analysis for
C1N2 (top) and GMSB (bottom) models.
Space below the solid red line is labelled as excluded and its dotted
neighbours show the result if all signal cross-sections are varied up and down
by theoretical error bars.
The yellow band shows the prior $\pm1$-sigma region of exclusion contours
from asymptotic approximations to the distribution of the test statistic.
Grey areas are observed limits from the $2\ell$ parts
of~\cite{SUSY-2016-24} and~\cite{SUSY-2013-11}.
Exclusion is defined by the $\mathrm{CLs}$ prescription at the $0.05$ level
in asymptotic approximations.
All contours are interpolated from a sparse grid.
}
\label{fig:2ljets_contours}
\end{figure}

>>>>

Our central result is Figure~\ref{fig:2ljets_summary}, which shows the names,
data, and fitted background expectations with error bars in all main regions.
This figure illustrates the background-model part of a \clown{likelihood}
function which is extended with signals to test alternative models.
Exclusion contours testing the addition of C1N2 and GMSB signals to these
backgrounds are shown in Figure~\ref{fig:2ljets_contours}.
Interpretations of discovery region data are displayed in
Table~\ref{tab:2ljets_discovery}.

% summary plot

@@

% exclusion plots

\begin{figure}[tp]
\centering
\begin{subfigure}{\textwidth}
    \centering
    \includegraphics[width=0.7\textwidth]{figures/2ljets_contours_c1n2.pdf}
    \caption{C1N2 contours}
\end{subfigure}
\\[1em]
\begin{subfigure}{\textwidth}
    \centering
    \includegraphics[width=0.7\textwidth]{figures/2ljets_contours_gmsb.pdf}
    \caption{GMSB contours}
\end{subfigure}
\caption{%
Contours from the $\twoljets$ electroweak analysis for
C1N2 (top) and GMSB (bottom) models.
Space below the solid red line is labelled as excluded and its dotted
neighbours show the result if all signal cross-sections are varied up and down
by theoretical error bars.
The yellow band shows the $\pm1$-sigma region of exclusion contours
from asymptotic approximations to the prior distribution of the test statistic.
Grey areas are observed limits from the two-lepton parts
of~\cite{SUSY-2016-24} and~\cite{SUSY-2013-11}.
Exclusion is defined by the $95\%$ $\mathrm{CLs}$ prescription
in asymptotic approximations.
All contours are interpolated from a sparse grid.
}
\label{fig:2ljets_contours}
\end{figure}

% upper limits
\begin{table}[tp]
\adjustbox{max width=0.98\textwidth}{%
\centering
\begin{tabular*}{\textwidth}{lccccccc}
{Region} &
\multicolumn{1}{c}{Fitted} &
\multicolumn{1}{l}{Data} &
$\langle A\epsilon{ \sigma}\rangle_{\mathrm{obs}}^{95}~\mathrm{fb}$ &
\multicolumn{1}{c}{$S_{\mathrm{obs}}^{95}$}  &
\multicolumn{1}{c}{$S_{\mathrm{exp}}^{95}$} &
$\mathrm{CLb}$ &
$p(s=0)~(Z)$  \\[1.5ex]
DR-OffShell      & $22.1\pm2.7$ & 21 & $0.10$ & $14.3$ & $12.3^{+4.7}_{-3.1}$ & $0.68$ & $0.50~(0.0)$ \\[.5ex]
DR-Low           & $22\pm4$ & 18 & $0.08$ & $10.8$ & $15.3^{+5.7}_{-4.0}$ & $0.09$ & $0.50~(0.0)$ \\[.5ex]
DR-Int           & $35\pm4$ & 38 & $0.15$ & $20.9$ & $17.5^{+5.9}_{-3.9}$ & $0.73$ & $0.23~(0.8)$ \\[.5ex]
DR-High          & $3.9\pm0.5$  & 0  & $0.02$ & $3.0$ & $5.6^{+2.2}_{-1.5}$ & $0.00$ & $0.50~(0.0)$ \\[.5ex]
DR-$\ell\ell bb$ & $0.51\pm0.20$  & 0  & $0.02$ & $3.0$ & $3.0^{+1.3}_{-0.0}$ & $0.19$ & $0.50~(0.0)$ \\[.5ex]
\end{tabular*}
}
\caption{%
Upper limit results in discovery region.
The fitted yield is in the background-only model constrained by the data in each region.
Limits are intended to reflect constrains on additive signal contributions.
\\[0.5em]
Left to right: the observed $95\%$ $\mathrm{CLs}$ upper limit on the visible cross-section
$\langle\epsilon\sigma\rangle_\mathrm{obs}^{95}$,
its corresponding signal expectation $S_\mathrm{obs}^{95}$,
expected $95\%$ upper limits on the signal expectation $S_\mathrm{exp}^{95}$
as would be obtained were the test statistic given by its central of $\pm 1$-sigma variations,
$\mathrm{CLb}$ evaluated with the signal expectation set to its observed upper limit,
and the discovery $p$-value capped at $0.5$ with its equivalent significance.
\\[0.5em]
Upper limits use the one-sided profile likelihood test statistic.
The discovery $p$-value uses a profile likelihood test statistic in a one-sided test.
All $p$-values are estimated by simulation of alternative data.
}
\label{tab:2ljets_discovery}
\end{table}
